\documentclass[letter,12pt]{report}

\begin{document}


\title{Software Engineering\\CEN 4010-U01\\Blue Jay\\Team 2\\Deliverable 1}
\author{David Ramirez\and Josselyn Ruiz\and Alex Collantes\and Mareo Yapp\and Brandon Lee}
\date{\today}
\maketitle

\tableofcontents

\begin{abstract}
\addcontentsline{toc}{chapter}{Abstract}
This document describes the basic structure of the Blue Jay project.
The primary goal is to clearly describe the design of the project,
and begin laying out the groundwork for how the system will be laid out
in the future.
\end{abstract}



\chapter{Introduction}
This chapter covers the basic knowledge needed to understand our project.

\section{Purpose of the System}
The Blue Jay system is a social media application,
remniniscent of twitter and reddit. It shares some of its
core functionality withe such systems, namely the ability for users
to create posts, reply to posts, browse posts, and view posts.


\section{Scope of the System}
The system is meant to be a simplified version of a social media platform.
Users can create posts, which will be publicly viewable by all other users.
Users can view posts, and from viewing posts reply to posts with their own
posts.
Users can access posts through browsing through recent posts, searching
through posts, or from the home page.



\section{Development Methodology}
This software is being developed under the Unified Software Development Process.
As part of the 

\section{Definitions, Acronyms, Abbreviations}

\section{Overview of Document}
This document is divided into several chapters.
Chapter 2, Current Systems, covers existing systems and how our system
is different from those.
Chapter 3, Project Plan, covers our current plan for the project,
how we plan to organize the project, and what we tools we will need for the project.
Chapter 4, Requirements Elicitation, covers possible use cases for the project,
and the ten use cases we plan to implement.
Chapter 5, Requirements Analysis, covers

Chapter 6, The Glossary, defines terms used in the document.

Chapter 7, Approvals,

Chapter 8, References,

\chapter{Current System}

\chapter{Project Plan}

\section{Project Organization}
INCLOMPLETE

\input{./projectPlan/HardwareSoftwareRequirements}
\newpage
\input{./projectPlan/ProjectSchedule}

\chapter{Requirements Elicitation}

\section{Use Cases}
The following section covers the varirous possible use cases
that could be implemented for the system.
\newpage
\input{./useCase/T3-BJ001-BrowsePosts}
\newpage
\input{./useCase/T3-BJ002-ViewPost}
\newpage


\section{Use Case Diagram}

\chapter{Requirements Analysis}

\section{Scenarios}

\section{Static Model}

\section{Dynamic Model}

\chapter{Glossary}

\chapter{Approvals}

\chapter{References}

\appendix
\chapter{Project Schedule}
\chapter{User Interface Designs}
\chapter{Meetings Diary}

\end{document}
