\subsection{T3-BJ001-Browse Posts}
\textbf{Use Case ID:} T3-BJ001-Browse Posts\\
\textbf{Use Case Level:} High-level\\
\textbf{Details:}
\begin{itemize}
    \item The homepage is to display all recently popular posts
    \item \textbf{Actor:} SM User
    \item \textbf{Pre-conditions:}
    \begin{itemize}
        \item User has internet access
        \item User has logged on.
    \end{itemize}
    \item \textbf{Description:}
    \begin{enumerate}
        \item User requests homepage
        \item System queries database for most popular posts within the last 24 hours
        \item Server constructs home page, showing most popular posts.
        \item Page is delivered to user browser.
        \item Browser displays homepage
    \end{enumerate}
    \item \textbf{Post-conditions:}
    \begin{itemize}
        \item Opening this page has no effect on the internal state of the server. The page is delivered to the client user/administrator.
    \end{itemize}
\end{itemize}
\textbf{Alternative Courses of Action:}
\begin{itemize}
    \item User searches for specific posts
    \item User checks his/her notifications
\end{itemize}
\textbf{Extensions:}
\begin{itemize}
    \item None
\end{itemize}
\textbf{Exceptions:}
\begin{itemize}
    \item Posts could not be retrieved.
\end{itemize}
\textbf{Concurrent Uses:}
\begin{itemize}
    \item None
\end{itemize}
\textbf{Related Use Cases:}
\begin{itemize}
    \item T3-BJ002-View Post
    \item T3-BJ003-View Profile
\end{itemize}
\textbf{Decision Support}
\begin{itemize}
    \item Frequency: 100 times per minute
    \item Criticality: High
    \item Risk: Medium
\end{itemize}
\textbf{Constraints:}
\begin{itemize}
    \item Usability: Average of about a minute for users to recognize and understand interface.
    \item Reliability: 99\% available.
    \item Performance: Page should load in less than a second.
    \item Supportability: Supported by browsers across multiple desktop and mobile devices.
\end{itemize}
\textbf{Modification History}
\begin{itemize}
    \item Owner: David Ramirez
    \item Initiation date: 8/27/2019
    \item Date last modified: 9/30/2019
\end{itemize}