\documentclass{report}

\begin{document}

\title{Software Engineering\\CEN 4010-U01\\Blue Jay\\Team 2\\Deliverable 2}
\author{David Ramirez\and Josselyn Ruiz\and Alex Collantes\and Mareo Yapp\and Brandon Lee}
\date{\today}
\maketitle

\begin{abstract}

\end{abstract}

\chapter{Introduction}
In this chapter we introduce the purpose of BlueJay, and the functional and non-functional requirements of the use cases implemented.

\section{Purpose of system}
The purpose of the BlueJay system to allow users to post text and images in a safe and secure manner to reduce the leaking of sensitive information, which can lead to fraud and identity theft. This will be done using many existing security techniques, such as password encryption, SSL encryption, and other safety measures that encourage users to prioritize securing their data.
\section{Requirements}
\section{Functional Requirements}
\begin{enumerate}
    \item The system will allow users to create an account (see use case BJ015 – Account Creation in Appendix A).
    \item The system will allow users to create and upload posts (see use case BJ004 – Create Post in Appendix A).
    \item The will allow users to reply to a post (see use case BJ006 – Reply to Post in Appendix A).
    \item The system will allow users to view posts on the site (see use case BJ002 – View Post in Appendix A).
    \item The system will allow users to browse most recent popular post (see use case BJ001 – Browse Post in Appendix A).
    \item The system will make users go through a process to access their account (see use case BJ021 – Login in Appendix A).
    \item The system will allow users to exit their accounts (see use case BJ022 – Logout in Appendix A).
    \item The system will allow users to go through a process to access their account if they forget their password (see use case BJS005 – Forgot Password in Appendix A).
    \item The system will make users go through a process to get their password by answering 3 security questions (see use case BJS006 – Security Questions in Appendix A).
    \item The system will send users an email asking them to verify their account (see use case BJS007 – Email Verification in Appendix A).
\end{enumerate}


\end{document}