\subsection{T3-BJ002-View Post}
\textbf{Use Case ID:} T3-BJ002-View Post\\
\textbf{Use Case Level:} High-level\\
\textbf{Details:}
\begin{itemize}
    \item 
    \item \textbf{Actor:} User
    \item \textbf{Pre-conditions:}
    \begin{itemize}
        \item User has internet access
        \item User has logged on.
    \end{itemize}
    \item \textbf{Description:}
    \begin{enumerate}
        \item User selects a post on the page while searching through the posts, or within any of the extensions of that functionality.
        \item The browser requests the page with the selected post.
        \item The post, and all posts replying to that post are queried from the database.
        \item The server constructs the page to display the posts.
        \item The server sends the page to the browser.
        \item The browser displays the page to the user.
    \end{enumerate}
    \item \textbf{Post-conditions:}
    \begin{itemize}
        \item Number of views on the post increases by one.
    \end{itemize}
\end{itemize}
\textbf{Alternative Courses of Action:}
\begin{itemize}
    \item N/A
\end{itemize}
\textbf{Extensions:}
\begin{itemize}
    \item N/A
\end{itemize}
\textbf{Exceptions:}
\begin{itemize}
    \item Post could not be retrieved.
\end{itemize}
\textbf{Concurrent Uses:}
\begin{itemize}
    \item None
\end{itemize}
\textbf{Related Use Cases:}
\begin{itemize}
    \item T3-BJ001-Browse Post
\end{itemize}
\textbf{Decision Support}
\begin{itemize}
    \item Frequency: 100 times per minute
    \item Criticality: High
    \item Risk: Medium
\end{itemize}
\textbf{Constraints:}
\begin{itemize}
    \item Usability: Average of 2 minutes for user to learn how to navigate pages and make posts
    \item Reliability:
    \item Performance:
    \item Supportability: Supported by browsers across multiple desktop and mobile devices.
    \item Implementation:
\end{itemize}
\textbf{Modification History}
\begin{itemize}
    \item Owner: David Ramirez
    \item Initiation date: 8/27/2019
    \item Date last modified: 9/30/2019
\end{itemize}